---
title: "Lp(a) Analysis"
author: "Kaif"
date: "2026-05-12"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    fig_width: 6
    fig_height: 4
---

# Knit

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Setup and Inclusion funnel

(up to Lp(a); age filter deferred until AFTER the outlier check)

```{r}
# Load required libraries
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(gtsummary)
library(gt)
library(car)
library(broom)
library(MASS)
library(nnet)
library(mediation)
library(flextable)
library(officer)
library(reshape2)
library(purrr)
library(GGally)
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)
library(glue)
library(scales)

# Set working directory and load raw data
setwd("K:/KINDER-FSCM/Forschung Lehre/Hand aufs Herz/Analysis/15062026_output_base")
df_raw <- read.csv("df_all_percentiles.csv")  

# Process participant inclusion funnel
n_total <- nrow(df_raw)                        

df <- df_raw %>% filter(blood_tested != 0)           
n_blood <- nrow(df)

df <- df %>% filter(!is.na(blood_value_lpa))        
n_lpa <- nrow(df)

df <- df %>% filter(age >= 9 & age <= 18)            
n_age <- nrow(df)

df <- df %>% filter(sex != "Diverse")                
n_sex <- nrow(df)

n_final <- nrow(df)                                  

cat("Total in raw dataset:        ", n_total, "\n")
cat("  -> blood tested:           ", n_blood, "  (dropped ", n_total - n_blood, ")\n", sep = "")
cat("  -> valid Lp(a):            ", n_lpa,   "  (dropped ", n_blood - n_lpa,  ")\n", sep = "")
cat("  -> age 9-18:               ", n_age,   "  (dropped ", n_lpa   - n_age,  ")\n", sep = "")
cat("  -> sex Male/Female:        ", n_sex,   "  (dropped ", n_age   - n_sex,  ")\n", sep = "")
cat("FINAL analysis sample:       ", n_final, "\n")

# Setup housekeeping and select required columns
df$id <- as.factor(df$id)
df1_backup <- df

df <- df %>% dplyr::select(
  "id", "sex", "who_bmi", "who_bmi_for_age_z", "age",
  "fam_heart_dis", "fam_heart_attack", "fam_young_heart_attack",
  "phy_act", "ern_mds", "time_screen_weekday", "time_screen_weekend",
  "blood_value_lpa", "ht",
  "time_sleep_weekday", "time_sleep_weekend",
  "bp_sys", "bp_dia", "systolic_bp_percentile", "diastolic_bp_percentile"
)

# Combine family history variables into a single feature
make_famhx <- function(d) {
  d %>% mutate(card_risk_fam_combined = case_when(
    fam_heart_dis == "Yes" | fam_heart_attack == "Yes" | fam_young_heart_attack == "Yes" ~ "Yes",
    fam_heart_dis == "No"  & fam_heart_attack == "No"  ~ "No",
    TRUE ~ NA_character_))
}
df     <- make_famhx(df)
df_raw <- make_famhx(df_raw)

cat("\n--- Family history (card_risk_fam_combined) ---\n")
table(df$card_risk_fam_combined, useNA = "ifany")

# Perform bias check comparing included versus excluded participants
included_ids <- df$id

compare_df <- df_raw %>%
  mutate(
    id     = as.factor(id),
    status = if_else(id %in% included_ids, "Included", "Excluded"),
    status = factor(status, levels = c("Included", "Excluded"))
  )

tab_bias <- compare_df %>%
  dplyr::select(age, sex, who_bmi, bp_sys, bp_dia, status) %>%
  tbl_summary(
    by        = status,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits    = all_continuous() ~ 1,
    label = list(
      age     ~ "Age (years)",
      sex     ~ "Sex",
      who_bmi ~ "WHO BMI category",
      bp_sys  ~ "Systolic BP (mmHg)",
      bp_dia  ~ "Diastolic BP (mmHg)"
    ),
    missing_text = "Missing"
  ) %>%
  add_p() %>%                        
  add_overall() %>%
  modify_header(label = "**Characteristic**") %>%
  modify_caption("**Supplementary Table. Included vs Excluded Participants**") %>%
  bold_labels()

tab_bias
```

# Lifestyle Score

Four components, each scored 0–1.

```{r}
# Inspect raw category labels for sleep
table(df$time_sleep_weekday, useNA = "ifany")
table(df$time_sleep_weekend, useNA = "ifany")

# Clean text labels and strip hours
df$time_sleep_weekday <- as.factor(df$time_sleep_weekday)
df$time_sleep_weekend <- as.factor(df$time_sleep_weekend)

df <- df %>% mutate(time_sleep_weekday = str_remove_all(time_sleep_weekday, " hours"))
df <- df %>% mutate(time_sleep_weekend = str_remove_all(time_sleep_weekend, " hours"))

df <- df %>% mutate(time_screen_weekend = str_replace(time_screen_weekend, "More than 8 hours", "9"))
df <- df %>% mutate(time_screen_weekend = str_remove_all(time_screen_weekend, " hours"))
df <- df %>% mutate(time_screen_weekend = str_remove_all(time_screen_weekend, " hour"))

df <- df %>% mutate(time_screen_weekday = str_replace(time_screen_weekday, "More than 8 hours", "9"))
df <- df %>% mutate(time_screen_weekday = str_remove_all(time_screen_weekday, " hours"))
df <- df %>% mutate(time_screen_weekday = str_remove_all(time_screen_weekday, " hour"))

# Map sleep bands to numeric hours
sleep_map <- function(x) {
  case_when(
    x == "< 5"                 ~ 4.5,
    x == "5-6"                 ~ 5.5,
    x == "6-7"                 ~ 6.5,
    x == "7-8"                 ~ 7.5,
    x == "8-9"                 ~ 8.5,
    grepl(">|9|more", x, ignore.case = TRUE) ~ 9.5,
    TRUE                       ~ NA_real_
  )
}

df$time_sleep_weekday <- sleep_map(df$time_sleep_weekday)
df$time_sleep_weekend <- sleep_map(df$time_sleep_weekend)

# Convert variables to numeric
df$time_screen_weekday <- as.numeric(df$time_screen_weekday)
df$time_screen_weekend <- as.numeric(df$time_screen_weekend)
df$time_sleep_weekday  <- as.numeric(df$time_sleep_weekday)
df$time_sleep_weekend  <- as.numeric(df$time_sleep_weekend)

# Calculate weighted weekday/weekend averages
df <- df %>%
  mutate(
    score_screen = case_when(
      !is.na(time_screen_weekday) & !is.na(time_screen_weekend) ~ (time_screen_weekday * 5 + time_screen_weekend * 2) / 7,
      !is.na(time_screen_weekday) & is.na(time_screen_weekend)  ~ time_screen_weekday,
      is.na(time_screen_weekday) & !is.na(time_screen_weekend)  ~ time_screen_weekend,
      TRUE ~ NA_real_
    ),
    score_sleep = case_when(
      !is.na(time_sleep_weekday) & !is.na(time_sleep_weekend) ~ (time_sleep_weekday * 5 + time_sleep_weekend * 2) / 7,
      !is.na(time_sleep_weekday) & is.na(time_sleep_weekend)  ~ time_sleep_weekday,
      is.na(time_sleep_weekday) & !is.na(time_sleep_weekend)  ~ time_sleep_weekend,
      TRUE ~ NA_real_
    )
  )

table(df$score_screen)
table(df$score_sleep)

# Create component flag for screen time risk
df$screen <- ifelse((df$age <= 11 & df$score_screen >= 1), 1,
             ifelse((df$age >= 12 & df$score_screen >= 3), 1, 0))

# Create component flag for sleep duration risk
df$sleep  <- ifelse((df$age <= 12 & df$score_sleep < 9), 1,
             ifelse((df$age >= 13 & df$score_sleep < 8), 1, 0))

table(df$screen, df$score_screen)
table(df$sleep,  df$score_sleep)

# Create component flag for Mediterranean diet score
table(df$ern_mds)
df$ern_mds_score <- case_when(
  is.na(df$ern_mds)                                             ~ NA_real_,
  grepl("<=\\s*3|≤\\s*3|\\b3\\b.*less|low", df$ern_mds, ignore.case = TRUE) ~ 1,
  TRUE                                                          ~ 0
)

table(df$ern_mds_score, df$ern_mds, useNA = "always")

# Create component flag for physical activity
table(df$phy_act, useNA = "always")

df$phy_act_score <- case_when(
  is.na(df$phy_act) ~ NA_real_,
  df$phy_act == 0   ~ 1,
  TRUE              ~ 0
)

table(df$phy_act_score, df$phy_act, useNA = "always")

# Calculate composite lifestyle score and categories
df$comp_score <- rowSums(cbind(df$screen, df$sleep, df$ern_mds_score, df$phy_act_score),
                         na.rm = FALSE)

df$comp_score_f <- factor(df$comp_score)

df$comp_score_cat <- factor(df$comp_score,
                            levels = 0:4,
                            labels = c("0 (best)", "1", "2", "3", "4 (worst)"),
                            ordered = TRUE)

table(df$comp_score_cat, useNA = "always")
table(df$comp_score,     useNA = "always")

# Create lifestyle tiers
df <- df %>%
  mutate(lifestyle_tier = case_when(
           comp_score <= 1 ~ "Ideal (0-1)",
           comp_score == 2 ~ "Moderate (2)",
           comp_score >= 3 ~ "Poor (3-4)",
           TRUE            ~ NA_character_
          ),
         lifestyle_tier = factor(lifestyle_tier,
                                 levels = c("Ideal (0-1)", "Moderate (2)", "Poor (3-4)")))

# Categorize blood pressure
elevated_levels <- c("P90", "P95", "P97", "P99")
normal_levels   <- c("<P50", "P50", "P75")

df <- df %>%
  mutate(bp_elevated = case_when(
    systolic_bp_percentile  %in% elevated_levels ~ "Elevated",
    diastolic_bp_percentile %in% elevated_levels ~ "Elevated",
    systolic_bp_percentile  %in% normal_levels &
      diastolic_bp_percentile %in% normal_levels ~ "Normal",
    TRUE ~ NA_character_
  ))

table(df$bp_elevated, useNA = "ifany")

# Prepare regression dataset and log transform Lp(a)
df <- df %>%
  mutate(
    log_lpa = ifelse(blood_value_lpa == 0, NA_real_, log(blood_value_lpa)),
    sex     = factor(sex)
  )

vars_all <- c("bp_sys", "bp_dia", "systolic_bp_percentile", "diastolic_bp_percentile",
              "log_lpa", "blood_value_lpa", "age", "sex", "who_bmi_for_age_z", 
              "card_risk_fam_combined", "comp_score", "comp_score_f", "lifestyle_tier",
              "phy_act_score", "ern_mds_score", "screen", "sleep", "ht")

missing_summary <- df %>%
  dplyr::select(all_of(vars_all)) %>%
  summarise(across(everything(), ~ sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "n_missing") %>%
  mutate(n_total = nrow(df),
         pct_missing = round(100 * n_missing / n_total, 1)) %>%
  arrange(desc(n_missing))

df_reg <- df[complete.cases(df[vars_all]), ]

df_reg$lifestyle_tier <- factor(
  df_reg$lifestyle_tier,
  levels = c("Ideal (0-1)", "Moderate (2)", "Poor (3-4)")
)
df_reg$screen        <- factor(df_reg$screen)
df_reg$sleep         <- factor(df_reg$sleep)
df_reg$ern_mds_score <- factor(df_reg$ern_mds_score)

cat("Total rows in original dataset:", nrow(df), "\n")
cat("Unified complete cases (df_reg) for ALL models:", nrow(df_reg), "\n")
cat("Dropped for missingness:", nrow(df) - nrow(df_reg), "\n")

# Fit linear models using composite score factors
m_factor_sys <- lm(bp_sys ~ comp_score_f + age + sex + who_bmi_for_age_z, data = df_reg)
m_factor_dia <- lm(bp_dia ~ comp_score_f + age + sex + who_bmi_for_age_z, data = df_reg)

summary(m_factor_sys)
summary(m_factor_dia)

# Perform data integrity checks
cat("Duplicate IDs in raw:", sum(duplicated(df_raw$id)), "\n")

cat("Distinct ages:", n_distinct(df$age), " range:", range(df$age, na.rm=TRUE), "\n")

df %>% summarise(
  bp_sys_le_dia = sum(bp_sys <= bp_dia, na.rm = TRUE),
  sbp_out       = sum(bp_sys < 60  | bp_sys > 200, na.rm = TRUE),
  dbp_out       = sum(bp_dia < 30  | bp_dia > 130, na.rm = TRUE),
  bmiz_out      = sum(abs(who_bmi_for_age_z) > 5, na.rm = TRUE),
  lpa_zero      = sum(blood_value_lpa == 0, na.rm = TRUE),
  lpa_max       = max(blood_value_lpa, na.rm = TRUE)
)

table(df$age, df$screen)
table(df$age, df$sleep)

cat("screen: weekday-only", sum(!is.na(df$time_screen_weekday) & is.na(df$time_screen_weekend)),
    " weekend-only", sum(is.na(df$time_screen_weekday) & !is.na(df$time_screen_weekend)), "\n")

df %>% summarise(across(c(screen, sleep, ern_mds_score, phy_act_score),
                        ~ sprintf("%d (%.1f%%)", sum(.x == 1, na.rm=TRUE),
                                  100*mean(.x == 1, na.rm=TRUE))))

stopifnot(!any(is.na(df$score_sleep)  & !is.na(df$time_sleep_weekday)))
stopifnot(!any(is.na(df$score_screen) & !is.na(df$time_screen_weekday)))

table(df_raw$sex, useNA = "ifany")

# Build final derived outcomes on the regression dataset
percentile_levels <- c("<P50","P50","P75","P90","P95","P97","P99")
elev <- c("P90","P95","P97","P99")

stopifnot(length(setdiff(na.omit(unique(df_reg$systolic_bp_percentile)),  percentile_levels)) == 0)
stopifnot(length(setdiff(na.omit(unique(df_reg$diastolic_bp_percentile)), percentile_levels)) == 0)

df_reg <- df_reg %>%
  mutate(
    sys_pctl_ord = factor(systolic_bp_percentile,  levels = percentile_levels, ordered = TRUE),
    dia_pctl_ord = factor(diastolic_bp_percentile, levels = percentile_levels, ordered = TRUE),

    sys_high90 = case_when(
      is.na(systolic_bp_percentile) | is.na(bp_sys)   ~ NA_real_,
      age <  13 & systolic_bp_percentile %in% elev    ~ 1,
      age >= 13 & bp_sys >= 120                      ~ 1,
      TRUE                                           ~ 0),
    dia_high90 = case_when(
      is.na(diastolic_bp_percentile) | is.na(bp_dia)  ~ NA_real_,
      age <  13 & diastolic_bp_percentile %in% elev   ~ 1,
      age >= 13 & bp_dia >= 80                       ~ 1,
      TRUE                                           ~ 0),

    sys_bp_cat3 = factor(case_when(
      systolic_bp_percentile %in% c("<P50","P50") ~ "<P75",
      systolic_bp_percentile == "P75"             ~ "P75-P90",
      systolic_bp_percentile %in% elev            ~ ">=P90"),
      levels = c("<P75","P75-P90",">=P90")),
    dia_bp_cat3 = factor(case_when(
      diastolic_bp_percentile %in% c("<P50","P50") ~ "<P75",
      diastolic_bp_percentile == "P75"             ~ "P75-P90",
      diastolic_bp_percentile %in% elev            ~ ">=P90"),
      levels = c("<P75","P75-P90",">=P90")),

    lpa_clinical_risk = factor(
      ifelse(blood_value_lpa >= 75, "High Risk (>=75)", "Normal (<75)"),
      levels = c("Normal (<75)", "High Risk (>=75)")),

    lifestyle_tier         = relevel(factor(lifestyle_tier), ref = "Ideal (0-1)"),
    card_risk_fam_combined = relevel(factor(card_risk_fam_combined), ref = "No")
  )

table(df_reg$sys_high90, useNA = "ifany")
table(df_reg$lifestyle_tier, df_reg$lpa_clinical_risk)

```

# Effects Model

Regression models

```{r}
# Define primary and secondary covariate sets
COV       <- "age + sex + who_bmi_for_age_z"        
COV_NOBMI <- "age + sex"                            
EXTRA     <- "log_lpa + card_risk_fam_combined"     

fit <- function(outcome, rhs, family = NULL) {
  f <- as.formula(paste(outcome, "~", rhs))
  if (is.null(family)) lm(f, data = df_reg) else glm(f, data = df_reg, family = family)
}

# Linear models for measured blood pressure
m1_sys <- fit("bp_sys", paste("log_lpa", COV, sep = " + "))
m1_dia <- fit("bp_dia", paste("log_lpa", COV, sep = " + "))
m2_sys <- fit("bp_sys", paste("log_lpa", COV, "comp_score + card_risk_fam_combined", sep = " + "))
m2_dia <- fit("bp_dia", paste("log_lpa", COV, "comp_score + card_risk_fam_combined", sep = " + "))
m3_sys <- fit("bp_sys", paste("log_lpa", COV, "phy_act_score + ern_mds_score + screen + sleep + card_risk_fam_combined", sep = " + "))
m3_dia <- fit("bp_dia", paste("log_lpa", COV, "phy_act_score + ern_mds_score + screen + sleep + card_risk_fam_combined", sep = " + "))
m4_sys <- fit("bp_sys", paste("log_lpa * card_risk_fam_combined", COV, "comp_score", sep = " + "))
m4_dia <- fit("bp_dia", paste("log_lpa * card_risk_fam_combined", COV, "comp_score", sep = " + "))

sys_main    <- fit("bp_sys", paste("lifestyle_tier", EXTRA, COV, sep = " + "))
dia_main    <- fit("bp_dia", paste("lifestyle_tier", EXTRA, COV, sep = " + "))
sys_lpa_int <- fit("bp_sys", paste("lifestyle_tier * log_lpa + card_risk_fam_combined", COV, sep = " + "))
dia_lpa_int <- fit("bp_dia", paste("lifestyle_tier * log_lpa + card_risk_fam_combined", COV, sep = " + "))
sys_fam_int <- fit("bp_sys", paste("lifestyle_tier * card_risk_fam_combined + log_lpa", COV, sep = " + "))
dia_fam_int <- fit("bp_dia", paste("lifestyle_tier * card_risk_fam_combined + log_lpa", COV, sep = " + "))

# BMI-free versions for total effect of lifestyle
sys_main_noBMI <- fit("bp_sys", paste("lifestyle_tier", EXTRA, COV_NOBMI, sep = " + "))
dia_main_noBMI <- fit("bp_dia", paste("lifestyle_tier", EXTRA, COV_NOBMI, sep = " + "))

# Height-adjusted parallel set of models
for (nm in c("m1_sys","m1_dia","m2_sys","m2_dia","m3_sys","m3_dia","m4_sys","m4_dia",
             "sys_main","dia_main","sys_lpa_int","dia_lpa_int","sys_fam_int","dia_fam_int")) {
  assign(paste0(nm, "_ht"), update(get(nm), . ~ . + ht))
}
stopifnot(nobs(sys_main) == nobs(sys_main_ht))   

# Logistic models using harmonized covariate set
sys90_main <- fit("sys_high90", paste("lifestyle_tier", EXTRA, COV, sep = " + "), family = binomial)
dia90_main <- fit("dia_high90", paste("lifestyle_tier", EXTRA, COV, sep = " + "), family = binomial)
sys90_lpa  <- fit("sys_high90", paste("lifestyle_tier * log_lpa + card_risk_fam_combined", COV, sep = " + "), family = binomial)
dia90_lpa  <- fit("dia_high90", paste("lifestyle_tier * log_lpa + card_risk_fam_combined", COV, sep = " + "), family = binomial)
sys90_fam  <- fit("sys_high90", paste("lifestyle_tier * card_risk_fam_combined + log_lpa", COV, sep = " + "), family = binomial)
dia90_fam  <- fit("dia_high90", paste("lifestyle_tier * card_risk_fam_combined + log_lpa", COV, sep = " + "), family = binomial)

# Multinomial models for BP categories
mn <- function(outcome, rhs) nnet::multinom(as.formula(paste(outcome, "~", rhs)),
                                            data = df_reg, trace = FALSE)
sys_main_cat    <- mn("sys_bp_cat3", paste("lifestyle_tier", EXTRA, COV, sep = " + "))
dia_main_cat    <- mn("dia_bp_cat3", paste("lifestyle_tier", EXTRA, COV, sep = " + "))
sys_lpa_int_cat <- mn("sys_bp_cat3", paste("lifestyle_tier * log_lpa + card_risk_fam_combined", COV, sep = " + "))
dia_lpa_int_cat <- mn("dia_bp_cat3", paste("lifestyle_tier * log_lpa + card_risk_fam_combined", COV, sep = " + "))
sys_fam_int_cat <- mn("sys_bp_cat3", paste("lifestyle_tier * card_risk_fam_combined + log_lpa", COV, sep = " + "))
dia_fam_int_cat <- mn("dia_bp_cat3", paste("lifestyle_tier * card_risk_fam_combined + log_lpa", COV, sep = " + "))

# Ordinal regression models
m_pctl_sys <- MASS::polr(as.formula(paste("sys_pctl_ord ~ comp_score_f", EXTRA, COV, sep = " + ")),
                         data = df_reg, Hess = TRUE)
m_pctl_dia <- MASS::polr(as.formula(paste("dia_pctl_ord ~ comp_score_f", EXTRA, COV, sep = " + ")),
                         data = df_reg, Hess = TRUE)

# Joint interaction tests using nested F-tests
int_tests <- bind_rows(
  broom::tidy(anova(sys_main, sys_lpa_int)) %>% mutate(Test = "Systolic: Lifestyle × Lp(a)"),
  broom::tidy(anova(dia_main, dia_lpa_int)) %>% mutate(Test = "Diastolic: Lifestyle × Lp(a)"),
  broom::tidy(anova(sys_main, sys_fam_int)) %>% mutate(Test = "Systolic: Lifestyle × FamHx"),
  broom::tidy(anova(dia_main, dia_fam_int)) %>% mutate(Test = "Diastolic: Lifestyle × FamHx")
) %>% filter(!is.na(statistic)) %>%
  transmute(Test, df, `Sum Sq` = round(sumsq, 2), `F statistic` = round(statistic, 2),
            `p-value` = ifelse(p.value < 0.001, "<0.001", sprintf("%.3f", p.value)))

ft_int_tests <- flextable(int_tests) %>%
  set_caption("Joint tests of effect modification (nested F-tests)") %>% autofit()
ft_int_tests

# Calculate minimum detectable interaction effects
mde <- function(model, label) {
  s <- summary(model)$coefficients
  rows <- grep(":", rownames(s), value = TRUE)
  if (!length(rows)) return(NULL)
  data.frame(Model = label, Term = rows, SE = round(s[rows,"Std. Error"], 3),
             `MDE (80% power)` = round(2.8 * s[rows,"Std. Error"], 2),
             check.names = FALSE, row.names = NULL)
}

mde_tab <- bind_rows(mde(sys_fam_int, "Sys: Lifestyle × FamHx"),
                     mde(dia_fam_int, "Dia: Lifestyle × FamHx"),
                     mde(sys_lpa_int, "Sys: Lifestyle × Lp(a)"),
                     mde(dia_lpa_int, "Dia: Lifestyle × Lp(a)"))

ft_mde <- flextable(mde_tab) %>%
  set_caption("Minimum detectable interaction effect (mmHg), 80% power, α = 0.05") %>% autofit()
ft_mde
```

# Descriptive BP by age, regression dataset (df_reg), and main-effects models

```{r}
# Calculate descriptive statistics for systolic blood pressure by age
bp_age <- df %>%
  group_by(age) %>%
  summarise(
    N        = sum(!is.na(bp_sys)),
    mean    = round(mean(bp_sys, na.rm = TRUE), 2),
    sd      = round(sd(bp_sys,   na.rm = TRUE), 2),
    se      = round(sd / sqrt(N), 2),
    min     = round(min(bp_sys,  na.rm = TRUE), 2),
    max     = round(max(bp_sys,  na.rm = TRUE), 2),
    IQR     = round(IQR(bp_sys,  na.rm = TRUE), 2),
    CI_low  = round(mean - qnorm(.975) * se, 2),
    CI_high = round(mean + qnorm(.975) * se, 2),
    .groups = "drop"
  )

bp_age
```


# Sensitivity Analyses

```{r}
# Sensitivity A: Binary Lp(a) Cutoff
sys_sens_bin_main <- fit("bp_sys", paste("lifestyle_tier + lpa_clinical_risk + card_risk_fam_combined", COV, sep = " + "))
sys_sens_bin_int  <- fit("bp_sys", paste("lifestyle_tier * lpa_clinical_risk + card_risk_fam_combined", COV, sep = " + "))

dia_sens_bin_main <- fit("bp_dia", paste("lifestyle_tier + lpa_clinical_risk + card_risk_fam_combined", COV, sep = " + "))
dia_sens_bin_int  <- fit("bp_dia", paste("lifestyle_tier * lpa_clinical_risk + card_risk_fam_combined", COV, sep = " + "))

# Sensitivity B: Continuous Lifestyle Score
sys_sens_cont_main    <- fit("bp_sys", paste("comp_score", EXTRA, COV, sep = " + "))
sys_sens_cont_lpa_int <- fit("bp_sys", paste("comp_score * log_lpa + card_risk_fam_combined", COV, sep = " + "))
sys_sens_cont_fam_int <- fit("bp_sys", paste("comp_score * card_risk_fam_combined + log_lpa", COV, sep = " + "))

dia_sens_cont_main    <- fit("bp_dia", paste("comp_score", EXTRA, COV, sep = " + "))
dia_sens_cont_lpa_int <- fit("bp_dia", paste("comp_score * log_lpa + card_risk_fam_combined", COV, sep = " + "))
dia_sens_cont_fam_int <- fit("bp_dia", paste("comp_score * card_risk_fam_combined + log_lpa", COV, sep = " + "))

# Build and display formatted sensitivity table
sens_tests <- bind_rows(
  broom::tidy(anova(sys_sens_bin_main, sys_sens_bin_int)) %>% mutate(Test = "Systolic: Binary Lp(a) Interaction"),
  broom::tidy(anova(dia_sens_bin_main, dia_sens_bin_int)) %>% mutate(Test = "Diastolic: Binary Lp(a) Interaction"),
  broom::tidy(anova(sys_sens_cont_main, sys_sens_cont_lpa_int)) %>% mutate(Test = "Systolic: Cont Lifestyle × Lp(a)"),
  broom::tidy(anova(dia_sens_cont_main, dia_sens_cont_lpa_int)) %>% mutate(Test = "Diastolic: Cont Lifestyle × Lp(a)"),
  broom::tidy(anova(sys_sens_cont_main, sys_sens_cont_fam_int)) %>% mutate(Test = "Systolic: Cont Lifestyle × FamHx"),
  broom::tidy(anova(dia_sens_cont_main, dia_sens_cont_fam_int)) %>% mutate(Test = "Diastolic: Cont Lifestyle × FamHx")
) %>% 
  filter(!is.na(statistic)) %>%
  transmute(Test, df, `Sum Sq` = round(sumsq, 2), `F statistic` = round(statistic, 2),
            `p-value` = ifelse(p.value < 0.001, "<0.001", sprintf("%.3f", p.value)))

ft_sens_tests <- flextable(sens_tests) %>%
  set_caption("Sensitivity Analyses: Effect Modification Models (ANOVA)") %>% 
  autofit()

ft_sens_tests
```


# Model Diagnostics

```{r fig.width=12, fig.height=6}
# Calculate Variance Inflation Factors for main-effects model
vif_sys <- car::vif(sys_main)

ft_vif <- as.data.frame(vif_sys) %>%
  tibble::rownames_to_column("Predictor") %>%
  flextable() %>%
  set_caption("Variance Inflation Factors (Main-Effects Model)") %>%
  autofit()

ft_vif

# Create diagnostic plots for model residuals
diag_data <- broom::augment(sys_main)

# Residuals vs Fitted plot to check for homoscedasticity
p_resid_fit <- ggplot(diag_data, aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.5, color = "#2166AC") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red", linewidth = 1) +
  geom_smooth(method = "loess", se = FALSE, color = "black") +
  theme_minimal(base_size = 14) +
  labs(title = "Residuals vs Fitted Values",
       subtitle = "Checking for Homoscedasticity",
       x = "Fitted Values (Predicted Systolic BP)",
       y = "Residuals")

# Normal Q-Q plot to check normality of residuals
p_qq <- ggplot(diag_data, aes(sample = .std.resid)) +
  stat_qq(alpha = 0.5, color = "#B2182B") +
  stat_qq_line(color = "black", linetype = "dashed", linewidth = 1) +
  theme_minimal(base_size = 14) +
  labs(title = "Normal Q-Q Plot",
       subtitle = "Checking Normality of Residuals",
       x = "Theoretical Quantiles",
       y = "Standardized Residuals")

p_resid_fit
p_qq

```

# Mediation analysis Poor lifestyle -\> BMI -\> Blood pressure

```{r}
# Create binary lifestyle indicator for poor tier vs ideal/moderate
df_reg$lifestyle_poor <- ifelse(df_reg$lifestyle_tier == "Poor (3-4)", 1, 0)

# Filter dataset for complete cases required by mediation models
med_vars <- c("bp_sys", "bp_dia", "who_bmi_for_age_z", "lifestyle_poor", "log_lpa", "age", "sex")
df_med <- df_reg[complete.cases(df_reg[med_vars]), ]

# Fit the a-path model for lifestyle predicting the mediator (BMI)
model_a <- lm(
  who_bmi_for_age_z ~ lifestyle_poor + log_lpa + age + sex,
  data = df_med
)

# Fit outcome models including both lifestyle and the BMI mediator
sys_med <- lm(
  bp_sys ~ lifestyle_poor + who_bmi_for_age_z + log_lpa + age + sex,
  data = df_med
)

dia_med <- lm(
  bp_dia ~ lifestyle_poor + who_bmi_for_age_z + log_lpa + age + sex,
  data = df_med
)

# Run bootstrapped mediation tests
set.seed(123)   

med_sys <- mediate(
  model.m  = model_a,
  model.y  = sys_med,
  treat    = "lifestyle_poor",
  mediator = "who_bmi_for_age_z",
  boot     = TRUE,
  sims     = 1000
)

med_dia <- mediate(
  model.m  = model_a,
  model.y  = dia_med,
  treat    = "lifestyle_poor",
  mediator = "who_bmi_for_age_z",
  boot     = TRUE,
  sims     = 1000
)

summary(med_sys)
summary(med_dia)

# Extract path coefficients for analysis and reporting
paths <- list(
  A = tidy(model_a) %>% filter(term == "lifestyle_poor"),

  SYS_total = tidy(
    lm(bp_sys ~ lifestyle_poor + log_lpa + age + sex,
       data = df_med)
  ) %>% filter(term == "lifestyle_poor"),

  SYS_direct = tidy(sys_med) %>% filter(term == "lifestyle_poor"),
  SYS_mediator = tidy(sys_med) %>% filter(term == "who_bmi_for_age_z"),

  DIA_total = tidy(
    lm(bp_dia ~ lifestyle_poor + log_lpa + age + sex,
       data = df_med)
  ) %>% filter(term == "lifestyle_poor"),

  DIA_direct = tidy(dia_med) %>% filter(term == "lifestyle_poor"),
  DIA_mediator = tidy(dia_med) %>% filter(term == "who_bmi_for_age_z")
)

paths

# Build and display formatted mediation table
ft_mediation <- bind_rows(paths, .id = "Path") %>%
  dplyr::select(Path, term, estimate, std.error, statistic, p.value) %>%
  mutate(across(c(estimate, std.error, statistic), ~round(.x, 3)),
         p.value = ifelse(as.numeric(p.value) < 0.001, "<0.001", sprintf("%.3f", as.numeric(p.value)))) %>%
  flextable() %>%
  set_caption("Mediation Analysis Paths (Lifestyle -> BMI -> BP)") %>%
  autofit()

ft_mediation
```

# BP \>= 90th percentile (binary outcomes) logistic models + odds-ratio forest plot

```{r fig.width=12, fig.height=8}
# Extract and combine main effects odds ratios for binary BP outcomes
main90_df <- bind_rows(
  tidy(sys90_main, conf.int = TRUE, exponentiate = TRUE) %>%
    mutate(outcome = "Systolic BP >=90th percentile",  analysis = "Main effects"),
  tidy(dia90_main, conf.int = TRUE, exponentiate = TRUE) %>%
    mutate(outcome = "Diastolic BP >=90th percentile", analysis = "Main effects")
)

# Extract and combine interaction effects odds ratios
int90_df <- bind_rows(
  tidy(sys90_lpa, conf.int = TRUE, exponentiate = TRUE) %>% filter(grepl(":", term)) %>%
    mutate(outcome = "Systolic BP >=90th percentile",  analysis = "Interactions"),
  tidy(dia90_lpa, conf.int = TRUE, exponentiate = TRUE) %>% filter(grepl(":", term)) %>%
    mutate(outcome = "Diastolic BP >=90th percentile", analysis = "Interactions"),
  tidy(sys90_fam, conf.int = TRUE, exponentiate = TRUE) %>% filter(grepl(":", term)) %>%
    mutate(outcome = "Systolic BP >=90th percentile",  analysis = "Interactions"),
  tidy(dia90_fam, conf.int = TRUE, exponentiate = TRUE) %>% filter(grepl(":", term)) %>%
    mutate(outcome = "Diastolic BP >=90th percentile", analysis = "Interactions")
)

# Combine datasets and clean term labels for plotting
plot_or_df <- bind_rows(main90_df, int90_df) %>%
  filter(term != "(Intercept)") %>%
  mutate(term = case_when(
    term == "lifestyle_tierModerate (2)" ~ "Moderate lifestyle",
    term == "lifestyle_tierPoor (3-4)"   ~ "Poor lifestyle",
    term == "screen1"                    ~ "Excessive screen time",
    term == "sleep1"                     ~ "Poor sleep",
    term == "ern_mds_score1"             ~ "Unhealthy diet",
    term == "log_lpa"                    ~ "Lp(a) (log)",
    term == "who_bmi_for_age_z"            ~ "BMI",
    grepl("Moderate.*log_lpa", term)     ~ "Moderate lifestyle × Lp(a)",
    grepl("Poor.*log_lpa",     term)     ~ "Poor lifestyle × Lp(a)",
    grepl("Moderate.*who_bmi_for_age_z", term)     ~ "Moderate lifestyle × BMI",
    grepl("Poor.*who_bmi_for_age_z",     term)     ~ "Poor lifestyle × BMI",
    TRUE ~ term
  ),
  analysis = factor(analysis, levels = c("Main effects", "Interactions")))

# Generate forest plot for binary BP outcomes
p_forest_binary <- ggplot(plot_or_df,
       aes(x = estimate, y = reorder(term, estimate),
           xmin = conf.low, xmax = conf.high,
           colour = outcome, group = outcome)) + 
  geom_vline(xintercept = 1, linetype = "dashed", colour = "grey50") +
  geom_errorbarh(height = 0.25, position = position_dodge(width = 0.6)) +
  geom_point(size = 3, position = position_dodge(width = 0.6)) +
  facet_wrap(~analysis, scales = "free_y", ncol = 2) +
  scale_colour_manual(values = c(
    "Systolic BP >=90th percentile" = "#2166AC",
    "Diastolic BP >=90th percentile" = "#B2182B")) +
  scale_x_log10(breaks = c(0.25, 0.5, 1, 2, 4)) + 
  labs(x = "Odds ratio (95% CI)", y = NULL, colour = "Outcome") +
  theme_bw(base_size = 16) +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(size = 14),
    axis.text.y = element_text(size = 15),
    axis.title = element_text(size = 16, face = "bold"),
    strip.text = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 15, face = "bold"),
    panel.spacing = unit(2, "lines")
  )

p_forest_binary
```

# BP in 3 categories (<P75 / P75-P90 / >=P90) multinomial models + odds-ratio forest plot

```{r fig.width=12, fig.height=10}
# Extract odds ratios for multinomial BP category models
main_cat_df <- bind_rows(
  tidy(sys_main_cat, exponentiate = TRUE, conf.int = TRUE) %>%
    mutate(outcome = "Systolic BP",  panel = "A: Main effects"),
  tidy(dia_main_cat, exponentiate = TRUE, conf.int = TRUE) %>%
    mutate(outcome = "Diastolic BP", panel = "A: Main effects")
)

int_cat_df <- bind_rows(
  tidy(sys_lpa_int_cat, exponentiate = TRUE, conf.int = TRUE) %>% filter(grepl(":", term)) %>%
    mutate(outcome = "Systolic BP",  panel = "B: Interactions"),
  tidy(dia_lpa_int_cat, exponentiate = TRUE, conf.int = TRUE) %>% filter(grepl(":", term)) %>%
    mutate(outcome = "Diastolic BP", panel = "B: Interactions"),
  tidy(sys_fam_int_cat, exponentiate = TRUE, conf.int = TRUE) %>% filter(grepl(":", term)) %>%
    mutate(outcome = "Systolic BP",  panel = "B: Interactions"),
  tidy(dia_fam_int_cat, exponentiate = TRUE, conf.int = TRUE) %>% filter(grepl(":", term)) %>%
    mutate(outcome = "Diastolic BP", panel = "B: Interactions")
)

plot_cat_df <- bind_rows(main_cat_df, int_cat_df) %>%
  filter(term != "(Intercept)")

# Relabel terms for plotting
plot_cat_df <- plot_cat_df %>%
  mutate(term = case_when(
    term == "lifestyle_tierModerate (2)"                     ~ "Moderate lifestyle",
    term == "lifestyle_tierPoor (3-4)"                      ~ "Poor lifestyle",
    term == "screen1"                                       ~ "Excessive screen",
    term == "sleep1"                                        ~ "Poor sleep",
    term == "ern_mds_score1"                                ~ "Unhealthy diet",
    term == "log_lpa"                                       ~ "Lp(a)",
    term == "who_bmi_for_age_z"                             ~ "BMI z-score",
    term == "lifestyle_tierModerate (2):log_lpa"            ~ "Moderate × Lp(a)",
    term == "lifestyle_tierPoor (3-4):log_lpa"              ~ "Poor × Lp(a)",
    term == "lifestyle_tierModerate (2):who_bmi_for_age_z"  ~ "Moderate × BMI",
    term == "lifestyle_tierPoor (3-4):who_bmi_for_age_z"    ~ "Poor × BMI",
    TRUE ~ term
  ))

# Generate multinomial forest plot
plot_cat_df$y.level <- factor(plot_cat_df$y.level, levels = c("P75-P90", ">=P90"))

p_forest_multi <- ggplot(plot_cat_df,
       aes(x = estimate, y = reorder(term, estimate),
           xmin = conf.low, xmax = conf.high,
           colour = outcome, group = outcome)) +       
  geom_vline(xintercept = 1, linetype = "dashed", colour = "grey50") +
  geom_errorbarh(height = 0.25, position = position_dodge(width = 0.6)) +
  geom_point(size = 3, position = position_dodge(width = 0.6)) +
  facet_grid(panel ~ y.level, scales = "free_y") +
  scale_colour_manual(values = c("Systolic BP" = "#2166AC", "Diastolic BP" = "#B2182B")) +
  scale_x_log10() +
  labs(x = "Odds ratio (95% CI)", y = NULL, colour = "BP outcome") +
  theme_bw(base_size = 18) +
  theme(
    legend.position  = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text        = element_text(size = 14),
    axis.text.y      = element_text(size = 15),
    strip.text       = element_text(size = 16, face = "bold")
  )

p_forest_multi
```

# Supplementary tables: Estimate + 95% CI

```{r}
# Helper function to tidy models into Estimate, 95% CI, and p-value format
tidy_ci <- function(model, model_label, exponentiate = FALSE) {
  broom::tidy(model, conf.int = TRUE, exponentiate = exponentiate) %>%
    filter(term != "(Intercept)") %>%
    transmute(
      Model    = model_label,
      Term     = term,
      Estimate = round(estimate, 3),
      `95% CI` = sprintf("%.2f, %.2f", conf.low, conf.high),
      `p-value` = ifelse(p.value < 0.001, "<0.001", sprintf("%.3f", p.value))
    )
}

# Task 5: Main linear BP models (effect in mmHg)
supp_linear <- bind_rows(
  tidy_ci(m1_sys, "Systolic  M1: Base"),
  tidy_ci(m2_sys, "Systolic  M2: + Lifestyle & Family Hx"),
  tidy_ci(m3_sys, "Systolic  M3: + Components"),
  tidy_ci(m4_sys, "Systolic  M4: Lp(a) x Family Hx"),
  tidy_ci(m1_dia, "Diastolic M1: Base"),
  tidy_ci(m2_dia, "Diastolic M2: + Lifestyle & Family Hx"),
  tidy_ci(m3_dia, "Diastolic M3: + Components"),
  tidy_ci(m4_dia, "Diastolic M4: Lp(a) x Family Hx")
)

ft_supp_linear <- flextable(supp_linear) %>%
  set_caption("Supplementary Table S1. Linear BP models — estimate (mmHg) and 95% CI") %>%
  autofit()
ft_supp_linear

# Task 6: Composite lifestyle score models (estimate + 95% CI)
df_reg$lifestyle_tier <- relevel(factor(df_reg$lifestyle_tier), ref = "Ideal (0-1)")

mc_sys_lin  <- lm(bp_sys ~ comp_score + log_lpa + age + sex + who_bmi_for_age_z, data = df_reg)
mc_sys_tier <- lm(bp_sys ~ lifestyle_tier + log_lpa + age + sex + who_bmi_for_age_z, data = df_reg)
mc_dia_lin  <- lm(bp_dia ~ comp_score + log_lpa + age + sex + who_bmi_for_age_z, data = df_reg)
mc_dia_tier <- lm(bp_dia ~ lifestyle_tier + log_lpa + age + sex + who_bmi_for_age_z, data = df_reg)

supp_composite <- bind_rows(
  tidy_ci(mc_sys_lin,  "Systolic  ~ comp_score (continuous)"),
  tidy_ci(mc_sys_tier, "Systolic  ~ lifestyle tier"),
  tidy_ci(mc_dia_lin,  "Diastolic ~ comp_score (continuous)"),
  tidy_ci(mc_dia_tier, "Diastolic ~ lifestyle tier"),
  tidy_ci(m_factor_sys, "Systolic  ~ comp_score (factor)"),
  tidy_ci(m_factor_dia, "Diastolic ~ comp_score (factor)")
)

ft_supp_composite <- flextable(supp_composite) %>%
  set_caption("Supplementary Table S2. Composite-score models — estimate and 95% CI") %>%
  autofit()
ft_supp_composite

# Task 7: Compare composite score vs individual components via nested F-test
mod_comp_sys       <- lm(bp_sys ~ comp_score + log_lpa + age + sex + who_bmi_for_age_z, data = df_reg)
mod_components_sys <- lm(bp_sys ~ screen + sleep + ern_mds_score + phy_act_score +
                           log_lpa + age + sex + who_bmi_for_age_z, data = df_reg)
mod_comp_dia       <- lm(bp_dia ~ comp_score + log_lpa + age + sex + who_bmi_for_age_z, data = df_reg)
mod_components_dia <- lm(bp_dia ~ screen + sleep + ern_mds_score + phy_act_score +
                           log_lpa + age + sex + who_bmi_for_age_z, data = df_reg)

comp_vs_components <- bind_rows(
  broom::tidy(anova(mod_comp_sys, mod_components_sys)) %>% mutate(Outcome = "Systolic BP"),
  broom::tidy(anova(mod_comp_dia, mod_components_dia)) %>% mutate(Outcome = "Diastolic BP")
) %>%
  mutate(Model = rep(c("Composite (equal weights)", "Components (free)"), 2),
         across(c(sumsq, statistic), ~ round(.x, 2)),
         p.value = ifelse(is.na(p.value), "-",
                          format.pval(p.value, digits = 3, eps = 0.001))) %>%
  dplyr::select(Outcome, Model, df, sumsq, statistic, p.value)

ft_comp_vs_components <- flextable(comp_vs_components) %>%
  set_caption("Supplementary Table S3. Composite score vs individual components (nested F-test)") %>%
  autofit()
ft_comp_vs_components

# Export the supplementary tables to a Word file
read_docx() %>%
  body_add_par("Supplementary Tables", style = "heading 1") %>%
  body_add_par("S1. Linear BP models (estimate + 95% CI)", style = "heading 2") %>%
  body_add_flextable(ft_supp_linear) %>% body_add_par("", style = "Normal") %>%
  body_add_par("S2. Composite-score models (estimate + 95% CI)", style = "heading 2") %>%
  body_add_flextable(ft_supp_composite) %>% body_add_par("", style = "Normal") %>%
  body_add_par("S3. Composite vs components (nested F-test)", style = "heading 2") %>%
  body_add_flextable(ft_comp_vs_components) %>%
  print(target = "supplementary_tables.docx")

cat("Wrote supplementary_tables.docx (S1, S2, S3)\n")
```

# Visualizations

```{r}
# Blood pressure by lifestyle score (systolic + diastolic)
p_bp_lifestyle <- df %>%
  dplyr::select(comp_score, bp_sys, bp_dia) %>%
  drop_na(comp_score) %>%
  pivot_longer(c(bp_sys, bp_dia), names_to = "bp_type", values_to = "bp") %>%
  drop_na(bp) %>%
  mutate(bp_type = factor(bp_type, levels = c("bp_sys", "bp_dia"),
                          labels = c("Systolic", "Diastolic"))) %>%
  ggplot(aes(factor(comp_score), bp, fill = factor(comp_score))) +
  geom_boxplot(alpha = 0.7) +
  facet_wrap(~bp_type, scales = "free_y") +
  scale_fill_viridis_d() +
  theme_minimal() +
  labs(title = "Blood Pressure by Lifestyle Score",
       x = "Lifestyle Score (0 = best, 4 = worst)",
       y = "Blood Pressure (mmHg)", fill = "Score")
p_bp_lifestyle

# Systolic BP by combined family history
p_bp_famhist <- df %>%
  drop_na(card_risk_fam_combined, bp_sys) %>%
  ggplot(aes(card_risk_fam_combined, bp_sys, fill = card_risk_fam_combined)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = c("No" = "#619CFF", "Yes" = "#F8766D")) +
  theme_minimal() +
  labs(title = "Systolic BP by Strong Family History",
       x = "Combined Family History", y = "Systolic Blood Pressure")
p_bp_famhist

# BMI Z-Score vs Lp(a)
p_bmi_lpa <- df %>%
  filter(blood_value_lpa > 0) %>%
  drop_na(who_bmi_for_age_z, blood_value_lpa) %>%
  ggplot(aes(x = blood_value_lpa, y = who_bmi_for_age_z)) +
  geom_point(alpha = 0.4, color = "#1B9E77") +
  geom_smooth(method = "lm", se = TRUE, color = "#D95F02") +
  scale_x_log10() +
  theme_minimal() +
  labs(title = "Spread of BMI Z-Score Across Lp(a)",
       x = "Lp(a), mg/L (log scale)", y = "BMI Z-Score")
p_bmi_lpa

# Lp(a) across age
p_lpa_age <- df %>%
  filter(blood_value_lpa > 0) %>%
  drop_na(age, blood_value_lpa) %>%
  ggplot(aes(x = age, y = blood_value_lpa)) +
  geom_point(alpha = 0.4, color = "#2C7FB8") +
  geom_smooth(method = "loess", se = TRUE, color = "#D95F02") +
  scale_y_log10() +
  scale_x_continuous(breaks = seq(6, 18, by = 1)) +
  theme_minimal() +
  labs(title = "Spread of Lp(a) Across Age (Up to 18 Years)",
       x = "Age (years)", y = "Lp(a), mg/L (log scale)")
p_lpa_age

# Family history across age (logistic trend)
p_famhist_age <- df %>%
  drop_na(age, card_risk_fam_combined) %>%
  mutate(fh_num = if_else(card_risk_fam_combined == "Yes", 1, 0)) %>%
  ggplot(aes(age, fh_num, color = card_risk_fam_combined)) +
  geom_jitter(height = 0.08, width = 0.2, alpha = 0.4) +
  geom_smooth(aes(group = 1), method = "glm",
              method.args = list(family = "binomial"),
              se = TRUE, color = "black") +
  scale_color_manual(values = c("No" = "#619CFF", "Yes" = "#F8766D")) +
  scale_y_continuous(breaks = c(0, 1), labels = c("No", "Yes")) +
  theme_minimal() +
  labs(title = "Family History Across Age",
       x = "Age (years)", y = "Family History", color = "Family History")
p_famhist_age

# Blood pressure across age (systolic + diastolic)
p_bp_age <- df %>%
  dplyr::select(age, bp_sys, bp_dia) %>%
  pivot_longer(c(bp_sys, bp_dia), names_to = "bp_type", values_to = "bp") %>%
  drop_na(age, bp) %>%
  mutate(bp_type = factor(bp_type, levels = c("bp_sys", "bp_dia"),
                          labels = c("Systolic", "Diastolic"))) %>%
  ggplot(aes(age, bp, color = bp_type)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE) +
  scale_color_manual(values = c("Systolic" = "#F8766D", "Diastolic" = "#619CFF")) +
  theme_minimal() +
  labs(title = "Spread of Blood Pressure Across Age",
       x = "Age (years)", y = "Blood Pressure (mmHg)", color = "BP Type")
p_bp_age

# Systolic BP across lifestyle score (scatter)
p_bp_score_scatter <- df %>%
  drop_na(comp_score, bp_sys) %>%
  ggplot(aes(x = comp_score, y = bp_sys)) +
  geom_jitter(alpha = 0.4, color = "#1B9E77", width = 0.2, height = 0) +
  geom_smooth(method = "lm", se = TRUE, color = "#D95F02") +
  scale_x_continuous(breaks = 0:4) +
  theme_minimal() +
  labs(title = "Systolic BP across Lifestyle Scores",
       x = "Total Lifestyle Score (0 = Best, 4 = Worst)",
       y = "Systolic Blood Pressure (mmHg)")
p_bp_score_scatter

# Systolic BP vs BMI Z-Score
p_bp_bmi <- df %>%
  drop_na(who_bmi_for_age_z, bp_sys) %>%
  ggplot(aes(x = who_bmi_for_age_z, y = bp_sys)) +
  geom_point(alpha = 0.4, color = "darkgray") +
  geom_smooth(method = "lm", se = TRUE, color = "blue") +
  theme_minimal() +
  labs(title = "Systolic BP vs. BMI Z-Score",
       x = "BMI Z-Score", y = "Systolic Blood Pressure (mmHg)")
p_bp_bmi

# Log Lp(a) vs Systolic BP
p_lpa_bp <- df %>%
  drop_na(log_lpa, bp_sys) %>%
  ggplot(aes(x = log_lpa, y = bp_sys)) +
  geom_point(alpha = 0.4, color = "purple") +
  geom_smooth(method = "lm", color = "black", se = TRUE) +
  theme_minimal() +
  labs(title = "Log Lp(a) vs Systolic BP",
       x = "Log Lp(a) (mg/L)", y = "Systolic BP (mmHg)")
p_lpa_bp

# Density of log Lp(a) by family history
p_lpa_density_fh <- df %>%
  drop_na(log_lpa, card_risk_fam_combined) %>%
  ggplot(aes(x = log_lpa, fill = card_risk_fam_combined)) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("No" = "#619CFF", "Yes" = "#F8766D")) +
  theme_minimal() +
  labs(title = "Density of Log Lp(a) by Family History",
       x = "Log Lp(a) (mg/L)", y = "Density", fill = "Family History")
p_lpa_density_fh

# Correlation matrix (continuous variables)
cor_data <- df %>%
  dplyr::select(age, who_bmi_for_age_z, bp_sys, bp_dia, log_lpa, comp_score) %>%
  drop_na() %>%
  cor() %>%
  as.data.frame() %>%
  tibble::rownames_to_column(var = "Var1") %>%
  pivot_longer(cols = -Var1, names_to = "Var2", values_to = "Correlation")

p_corr <- ggplot(cor_data, aes(Var1, Var2, fill = Correlation)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white",
                       midpoint = 0, limit = c(-1, 1), space = "Lab",
                       name = "Pearson\nCorrelation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  labs(title = "Correlation Matrix of Key Continuous Variables", x = "", y = "")
p_corr

# Systolic BP across individual lifestyle components (violin)
p_bp_components <- df %>%
  dplyr::select(bp_sys, phy_act_score, ern_mds_score, screen, sleep) %>%
  drop_na() %>%
  pivot_longer(cols = c(phy_act_score, ern_mds_score, screen, sleep),
               names_to = "Component", values_to = "Score") %>%
  mutate(Component = recode(Component,
                            "phy_act_score" = "Physical Activity",
                            "ern_mds_score" = "Diet",
                            "screen" = "Screen Time",
                            "sleep" = "Sleep")) %>%
  ggplot(aes(x = factor(Score), y = bp_sys, fill = factor(Score))) +
  geom_violin(alpha = 0.6, trim = FALSE) +
  geom_boxplot(width = 0.1, fill = "white", outlier.shape = NA) +
  facet_wrap(~Component, scales = "free_x") +
  scale_fill_viridis_d() +
  theme_minimal() +
  labs(title = "Systolic BP Across Individual Lifestyle Components",
       x = "Component Risk Flag (0 = meets guideline, 1 = doesn't)",
       y = "Systolic BP (mmHg)", fill = "Score")
p_bp_components

# Overall spread of Lp(a) in the whole dataset (histogram)
p_lpa_spread_all <- df_raw %>%
  filter(blood_value_lpa > 0) %>%
  ggplot(aes(x = blood_value_lpa)) +
  geom_histogram(bins = 40, fill = "#2C7FB8", color = "white", alpha = 0.85) +
  scale_x_log10() +
  theme_minimal() +
  labs(title = "Overall Spread of Lp(a) (Whole Dataset)",
       x = "Lp(a), mg/L (log scale)", y = "Count")
p_lpa_spread_all

# Lp(a) vs log Lp(a): raw skew vs log-transformed, side by side
p_lpa_vs_log <- df %>%
  filter(blood_value_lpa > 0) %>%
  dplyr::select(blood_value_lpa, log_lpa) %>%
  pivot_longer(everything(), names_to = "scale", values_to = "value") %>%
  mutate(scale = recode(scale,
                        "blood_value_lpa" = "Raw Lp(a) (mg/L)",
                        "log_lpa"         = "Log Lp(a)")) %>%
  ggplot(aes(x = value, fill = scale)) +
  geom_histogram(bins = 40, color = "white", alpha = 0.85) +
  facet_wrap(~scale, scales = "free") +
  scale_fill_manual(values = c("Raw Lp(a) (mg/L)" = "#F8766D", "Log Lp(a)" = "#1B9E77")) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Lp(a): Raw vs Log-Transformed Distribution",
       x = "Value", y = "Count")
p_lpa_vs_log

# Family history: whole dataset vs analysis sample
fh_compare <- bind_rows(
  df_raw %>% mutate(dataset = "Whole dataset") %>% dplyr::select(dataset, card_risk_fam_combined),
  df     %>% mutate(dataset = "Analysis sample") %>% dplyr::select(dataset, card_risk_fam_combined)
) %>%
  mutate(card_risk_fam_combined = if_else(is.na(card_risk_fam_combined),
                                        "Unknown", card_risk_fam_combined),
         dataset = factor(dataset, levels = c("Whole dataset", "Analysis sample")))

p_fh_compare <- fh_compare %>%
  count(dataset, card_risk_fam_combined) %>%
  group_by(dataset) %>%
  mutate(pct = 100 * n / sum(n)) %>%
  ggplot(aes(x = card_risk_fam_combined, y = pct, fill = dataset)) +
  geom_col(position = "dodge", alpha = 0.85) +
  scale_fill_manual(values = c("Whole dataset" = "#9E9E9E", "Analysis sample" = "#1A9850")) +
  theme_minimal() +
  labs(title = "Family History Spread: Whole vs Analysis",
       x = "Family History", y = "Percentage (%)", fill = "Dataset")
p_fh_compare

# Lifestyle score spread — analysis sample only
p_lifestyle_spread <- df %>%
  drop_na(comp_score) %>%
  count(comp_score) %>%
  mutate(pct = 100 * n / sum(n)) %>%
  ggplot(aes(x = factor(comp_score), y = pct)) +
  geom_col(fill = "#1B9E77", alpha = 0.85) +
  geom_text(aes(label = paste0(round(pct, 1), "%")), vjust = -0.4, size = 3) +
  theme_minimal() +
  labs(title = "Lifestyle Score Spread (Analysis Sample)",
       x = "Lifestyle Score (0 = best, 4 = worst)", y = "Percentage (%)")
p_lifestyle_spread

# Included vs Excluded comparisons
compare_df <- df_raw %>%
  mutate(id = as.factor(id),
         status = if_else(id %in% df$id, "Included", "Excluded"),
         status = factor(status, levels = c("Included", "Excluded")))

# Age spread
p_excl_age <- compare_df %>%
  drop_na(age) %>%
  ggplot(aes(x = age, fill = status)) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("Included" = "#1A9850", "Excluded" = "#9E9E9E")) +
  theme_minimal() +
  labs(title = "Age: Included vs Excluded", x = "Age (years)", y = "Density", fill = NULL)
p_excl_age

# BMI spread
p_excl_bmi <- compare_df %>%
  drop_na(who_bmi_for_age_z) %>%
  ggplot(aes(x = who_bmi_for_age_z, fill = status)) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("Included" = "#1A9850", "Excluded" = "#9E9E9E")) +
  theme_minimal() +
  labs(title = "BMI Z-Score: Included vs Excluded",
       x = "BMI Z-Score", y = "Density", fill = NULL)
p_excl_bmi

# Systolic + diastolic BP spread
p_excl_bp <- compare_df %>%
  dplyr::select(status, bp_sys, bp_dia) %>%
  pivot_longer(c(bp_sys, bp_dia), names_to = "bp_type", values_to = "bp") %>%
  drop_na(bp) %>%
  mutate(bp_type = recode(bp_type, "bp_sys" = "Systolic", "bp_dia" = "Diastolic")) %>%
  ggplot(aes(x = status, y = bp, fill = status)) +
  geom_boxplot(alpha = 0.7) +
  facet_wrap(~bp_type, scales = "free_y") +
  scale_fill_manual(values = c("Included" = "#1A9850", "Excluded" = "#9E9E9E")) +
  theme_minimal() +
  labs(title = "Blood Pressure: Included vs Excluded",
       x = NULL, y = "Blood Pressure (mmHg)", fill = NULL)
p_excl_bp

# Sex distribution
p_excl_sex <- compare_df %>%
  drop_na(sex) %>%
  filter(sex != "Diverse") %>%
  count(status, sex) %>%
  group_by(status) %>%
  mutate(pct = 100 * n / sum(n)) %>%
  ggplot(aes(x = sex, y = pct, fill = status)) +
  geom_col(position = "dodge", alpha = 0.85) +
  scale_fill_manual(values = c("Included" = "#1A9850", "Excluded" = "#9E9E9E")) +
  theme_minimal() +
  labs(title = "Sex: Included vs Excluded",
       x = "Sex", y = "Percentage (%)", fill = NULL)
p_excl_sex

# Histograms: spread of continuous variables
p_hist_continuous <- df %>%
  dplyr::select(age, who_bmi_for_age_z, bp_sys, bp_dia, log_lpa) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Value") %>%
  drop_na(Value) %>%
  mutate(Variable = recode(Variable,
                           "age" = "Age", "bp_sys" = "Systolic BP",
                           "bp_dia" = "Diastolic BP", "log_lpa" = "Log Lp(a)",
                           "who_bmi_for_age_z" = "BMI Z-Score")) %>%
  ggplot(aes(x = Value, fill = Variable)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~Variable, scales = "free") +
  scale_fill_viridis_d() +
  theme_minimal() + theme(legend.position = "none") +
  labs(title = "Distribution of Key Continuous Variables",
       x = "Value", y = "Frequency Count")
p_hist_continuous

# Bar charts: spread of categorical variables
p_bar_categorical <- df %>%
  dplyr::select(sex, card_risk_fam_combined, comp_score) %>%
  mutate(comp_score = as.character(comp_score)) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Category") %>%
  drop_na(Category) %>%
  mutate(Variable = recode(Variable,
                           "card_risk_fam_combined" = "Family History of CVD",
                           "comp_score" = "Composite Score", "sex" = "Sex")) %>%
  ggplot(aes(x = Category, fill = Category)) +
  geom_bar(alpha = 0.8, color = "black") +
  facet_wrap(~Variable, scales = "free") +
  scale_fill_viridis_d(option = "plasma") +
  theme_minimal() +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Count of Categorical Variables",
       x = "Category", y = "Number of Participants")
p_bar_categorical

# Lp(a) vs continuous variables (faceted scatter)
p_lpa_vs_continuous <- df %>%
  filter(blood_value_lpa > 0) %>%
  dplyr::select(blood_value_lpa, age, who_bmi_for_age_z, bp_sys, bp_dia) %>%
  pivot_longer(cols = c(age, who_bmi_for_age_z, bp_sys, bp_dia),
               names_to = "Variable", values_to = "Value") %>%
  drop_na() %>%
  mutate(Variable = recode(Variable,
                           "age" = "Age", "bp_sys" = "Systolic BP",
                           "bp_dia" = "Diastolic BP", "who_bmi_for_age_z" = "BMI Z-Score")) %>%
  ggplot(aes(x = blood_value_lpa, y = Value)) +
  geom_point(alpha = 0.2, color = "#2C7FB8") +
  geom_smooth(method = "lm", color = "#D95F02", se = TRUE) +
  scale_x_log10() +
  facet_wrap(~Variable, scales = "free_y") +
  theme_minimal() +
  labs(title = "Lp(a) vs. Continuous Variables",
       x = "Lp(a), mg/L (log scale)", y = "Variable Value")
p_lpa_vs_continuous

# Lp(a) vs categorical variables (faceted boxplot)
p_lpa_vs_categorical <- df %>%
  filter(blood_value_lpa > 0) %>%
  dplyr::select(blood_value_lpa, sex, card_risk_fam_combined, comp_score) %>%
  mutate(comp_score = as.character(comp_score)) %>%
  pivot_longer(cols = c(sex, card_risk_fam_combined, comp_score),
               names_to = "Variable", values_to = "Category") %>%
  drop_na() %>%
  mutate(Variable = recode(Variable, "sex" = "Sex",
                           "card_risk_fam_combined" = "Family History of CVD",
                           "comp_score" = "Composite Score")) %>%
  ggplot(aes(x = Category, y = blood_value_lpa, fill = Category)) +
  geom_boxplot(alpha = 0.7, outlier.alpha = 0.4) +
  scale_y_log10() +
  facet_wrap(~Variable, scales = "free_x") +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Spread of Lp(a) Across Categories",
       x = "Category", y = "Lp(a), mg/L (log scale)")
p_lpa_vs_categorical

# Lp(a) developmental trajectory (smooth only)
p_lpa_trajectory <- df %>%
  filter(blood_value_lpa > 0) %>%
  drop_na(age, blood_value_lpa) %>%
  ggplot(aes(x = age, y = blood_value_lpa)) +
  geom_smooth(method = "loess", se = TRUE, color = "#D95F02", fill = "gray80") +
  scale_y_log10() +
  theme_minimal() +
  labs(title = "Developmental Trajectory of Lp(a)",
       x = "Age (years)", y = "Lp(a), mg/L (log scale)")
p_lpa_trajectory

# Lp(a) density by sex
p_lpa_density_sex <- df %>%
  filter(blood_value_lpa > 0) %>%
  drop_na(sex) %>%
  ggplot(aes(x = blood_value_lpa, fill = sex, color = sex)) +
  geom_density(alpha = 0.4) +
  scale_x_log10() +
  scale_fill_manual(values = c("female" = "#F8766D", "male" = "#619CFF")) +
  scale_color_manual(values = c("female" = "#F8766D", "male" = "#619CFF")) +
  theme_minimal() +
  labs(title = "Lp(a) Distribution by Sex",
       x = "Lp(a), mg/L (log scale)", y = "Density", fill = "Sex", color = "Sex")
p_lpa_density_sex

# Lp(a) by family history (boxplot + jitter)
p_lpa_famhist_box <- df %>%
  filter(blood_value_lpa > 0) %>%
  drop_na(card_risk_fam_combined) %>%
  ggplot(aes(x = card_risk_fam_combined, y = blood_value_lpa, fill = card_risk_fam_combined)) +
  geom_boxplot(alpha = 0.6, outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.3, size = 1.5) +
  scale_y_log10() +
  scale_fill_manual(values = c("No" = "#619CFF", "Yes" = "#F8766D")) +
  theme_minimal() +
  labs(title = "Lp(a) by Family History of CVD",
       x = "Family History", y = "Lp(a), mg/L (log scale)", fill = "Family History")
p_lpa_famhist_box

# Lp(a) by lifestyle tier (violin + boxplot)
p_lpa_tier <- df %>%
  filter(blood_value_lpa > 0) %>%
  drop_na(lifestyle_tier) %>%
  ggplot(aes(x = lifestyle_tier, y = blood_value_lpa, fill = lifestyle_tier)) +
  geom_violin(alpha = 0.5, trim = FALSE) +
  geom_boxplot(width = 0.15, alpha = 0.8, outlier.shape = NA) +
  scale_y_log10() +
  scale_fill_manual(values = c("Ideal (0-1)" = "#1A9850", "Moderate (2)" = "#FEE08B",
                               "Poor (3-4)" = "#D73027")) +
  theme_minimal() +
  labs(title = "Lp(a) Levels by Lifestyle Tier",
       subtitle = "Violin + boxplot; log scale",
       x = "Lifestyle Tier", y = "Lp(a), mg/L (log scale)", fill = "Lifestyle Tier")
p_lpa_tier

# Spearman correlation heatmap
cont_vars <- df %>%
  dplyr::select(blood_value_lpa, log_lpa, bp_sys, bp_dia, age, who_bmi_for_age_z,
                comp_score, time_screen_weekday, time_screen_weekend) %>%
  rename("Lp(a)" = blood_value_lpa, "log Lp(a)" = log_lpa,
         "Systolic BP" = bp_sys, "Diastolic BP" = bp_dia, "Age" = age,
         "BMI z-score" = who_bmi_for_age_z, "Lifestyle Score" = comp_score,
         "Screen (weekday)" = time_screen_weekday,
         "Screen (weekend)" = time_screen_weekend)

cor_mat  <- cor(cont_vars, use = "pairwise.complete.obs", method = "spearman")
cor_melt <- melt(cor_mat)

p_spearman_heatmap <- ggplot(cor_melt, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value, 2)), size = 2.8) +
  scale_fill_gradient2(low = "#2166AC", mid = "white", high = "#D6604D",
                       midpoint = 0, limits = c(-1, 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Spearman Correlation Heatmap", x = NULL, y = NULL, fill = "r")
p_spearman_heatmap

# BMI z-score distribution by sex
p_bmi_by_sex <- df %>%
  drop_na(who_bmi_for_age_z, sex) %>%
  ggplot(aes(x = who_bmi_for_age_z, fill = sex)) +
  geom_histogram(binwidth = 0.3, alpha = 0.6, position = "identity") +
  geom_vline(xintercept = c(-2, 1, 2), linetype = "dashed",
             color = c("blue", "orange", "red"), linewidth = 0.7) +
  scale_fill_manual(values = c("female" = "#F8766D", "male" = "#619CFF")) +
  theme_minimal() +
  labs(title = "BMI z-score Distribution by Sex",
       subtitle = "Dashed: z = -2 (underweight), +1 (overweight), +2 (obese)",
       x = "WHO BMI-for-age z-score", y = "Count", fill = "Sex")
p_bmi_by_sex

# BMI z-score vs Lp(a) (loess)
p_bmi_vs_lpa <- df %>%
  filter(blood_value_lpa > 0) %>%
  drop_na(who_bmi_for_age_z) %>%
  ggplot(aes(x = who_bmi_for_age_z, y = blood_value_lpa)) +
  geom_point(alpha = 0.35, color = "#2C7FB8") +
  geom_smooth(method = "loess", se = TRUE, color = "#D95F02") +
  scale_y_log10() +
  theme_minimal() +
  labs(title = "BMI z-score vs Lp(a)",
       x = "WHO BMI-for-age z-score", y = "Lp(a), mg/L (log scale)")
p_bmi_vs_lpa

# Coefficient plot: compare systolic models
tidy_models_sys <- bind_rows(
  tidy(m1_sys, conf.int = TRUE) %>% mutate(model = "M1: Base"),
  tidy(m2_sys, conf.int = TRUE) %>% mutate(model = "M2: + Family Hx"),
  tidy(m3_sys, conf.int = TRUE) %>% mutate(model = "M3: + Lifestyle")
)

p_coef_sys <- tidy_models_sys %>%
  filter(term != "(Intercept)") %>%
  ggplot(aes(x = estimate, y = term, color = model, xmin = conf.low, xmax = conf.high)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_pointrange(position = position_dodge(width = 0.5), size = 0.6) +
  scale_color_manual(values = c("M1: Base" = "#2166AC", "M2: + Family Hx" = "#F8766D",
                                "M3: + Lifestyle" = "#1A9850")) +
  theme_minimal() +
  labs(title = "Coefficient Plot: Systolic BP Models",
       x = "Estimate (mmHg)", y = "Predictor", color = "Model")
p_coef_sys

# Lifestyle x family history interaction
p_interaction <- df %>%
  drop_na(comp_score, card_risk_fam_combined, bp_sys) %>%
  ggplot(aes(x = comp_score, y = bp_sys,
             color = card_risk_fam_combined, fill = card_risk_fam_combined)) +
  geom_point(alpha = 0.25) +
  geom_smooth(method = "lm", se = TRUE, alpha = 0.15) +
  scale_color_manual(values = c("No" = "#619CFF", "Yes" = "#F8766D")) +
  scale_fill_manual(values = c("No" = "#619CFF", "Yes" = "#F8766D")) +
  theme_minimal() +
  labs(title = "Lifestyle Score x Family History on Systolic BP",
       x = "Lifestyle Score (0-4)", y = "Systolic BP (mmHg)",
       color = "Family History", fill = "Family History")
p_interaction

# Elevated Lp(a) prevalence by lifestyle tier
df <- df %>%
  mutate(lpa_elevated = case_when(
    blood_value_lpa >= 75 ~ "Elevated (>=75 nmol/L)",
    blood_value_lpa >= 0  ~ "Normal (<75 nmol/L)",
    TRUE ~ NA_character_
  ))

p_lpa_elevated_tier <- df %>%
  drop_na(lpa_elevated, lifestyle_tier) %>%
  count(lifestyle_tier, lpa_elevated) %>%
  group_by(lifestyle_tier) %>%
  mutate(pct = n / sum(n) * 100) %>%
  ggplot(aes(x = lifestyle_tier, y = pct, fill = lpa_elevated)) +
  geom_col(position = "stack", alpha = 0.85) +
  scale_fill_manual(values = c("Elevated (>=75 nmol/L)" = "#D73027",
                               "Normal (<75 nmol/L)" = "#91BFDB")) +
  theme_minimal() +
  labs(title = "Prevalence of Elevated Lp(a) by Lifestyle Tier",
       x = "Lifestyle Tier", y = "Percentage (%)", fill = "Lp(a) Status")
p_lpa_elevated_tier      

# Blood pressure across age, coloured by sex
p_bp_age_sex <- df %>%
  dplyr::select(age, sex, bp_sys, bp_dia) %>%
  pivot_longer(c(bp_sys, bp_dia), names_to = "bp_type", values_to = "bp") %>%
  drop_na(age, bp, sex) %>%
  mutate(bp_type = factor(bp_type, levels = c("bp_sys", "bp_dia"),
                          labels = c("Systolic", "Diastolic"))) %>%
  ggplot(aes(x = age, y = bp, color = sex)) +
  geom_jitter(width = 0.2, alpha = 0.4, size = 1.5) +
  geom_smooth(method = "lm", se = TRUE, linewidth = 1) +
  facet_wrap(~bp_type, scales = "free_y") +
  scale_color_manual(values = c("female" = "#F8766D", "male" = "#619CFF")) +
  scale_x_continuous(breaks = seq(9, 18, by = 1)) +
  theme_minimal(base_size = 13) +
  labs(title = "Blood Pressure Across Age by Sex",
       x = "Age (years)", y = "Blood Pressure (mmHg)", color = "Sex")
p_bp_age_sex

# Log Lp(a) vs systolic BP, split by lifestyle tier
p_lpa_bp_tier <- df %>%
  drop_na(log_lpa, bp_sys, lifestyle_tier) %>%
  ggplot(aes(x = log_lpa, y = bp_sys, color = lifestyle_tier)) +
  geom_point(alpha = 0.35, size = 1.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_wrap(~lifestyle_tier) +
  scale_color_manual(values = c("Ideal (0-1)" = "#1A9850", "Moderate (2)" = "#E6AB02",
                                "Poor (3-4)" = "#D73027")) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none") +
  labs(title = "Lp(a)-Blood Pressure Relationship by Lifestyle Tier",
       x = "Log Lp(a) (mg/L)", y = "Systolic BP (mmHg)")
p_lpa_bp_tier

# Raincloud: systolic BP across lifestyle score
p_bp_raincloud <- df %>%
  drop_na(comp_score, bp_sys) %>%
  ggplot(aes(x = factor(comp_score), y = bp_sys, fill = factor(comp_score))) +
  geom_violin(alpha = 0.5, trim = FALSE, width = 0.9) +
  geom_boxplot(width = 0.12, fill = "white", outlier.shape = NA, alpha = 0.8) +
  geom_jitter(width = 0.08, alpha = 0.25, size = 1) +
  scale_fill_viridis_d() +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none") +
  labs(title = "Distribution of Systolic BP Across Lifestyle Score",
       x = "Lifestyle Score (0 = best, 4 = worst)", y = "Systolic BP (mmHg)")
p_bp_raincloud

# Bubble chart: 4 variables in 2D
p_bubble <- df %>%
  filter(blood_value_lpa > 0) %>%
  drop_na(age, bp_sys, blood_value_lpa, lifestyle_tier) %>%
  ggplot(aes(x = age, y = bp_sys, size = blood_value_lpa, color = lifestyle_tier)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(range = c(1, 9), trans = "log10", name = "Lp(a)") +
  scale_color_manual(values = c("Ideal (0-1)" = "#1A9850", "Moderate (2)" = "#E6AB02",
                                "Poor (3-4)" = "#D73027"), name = "Lifestyle tier") +
  theme_minimal(base_size = 13) +
  labs(title = "Age, Blood Pressure, Lp(a) and Lifestyle in One View",
       x = "Age (years)", y = "Systolic BP (mmHg)")
p_bubble

# Pairs plot: all key continuous variables at once
p_pairs <- df %>%
  filter(blood_value_lpa > 0) %>%
  dplyr::select(age, who_bmi_for_age_z, bp_sys, bp_dia, log_lpa, comp_score, sex) %>%
  drop_na() %>%
  ggpairs(
    columns = 1:6,
    mapping = aes(color = sex, alpha = 0.5),
    upper = list(continuous = wrap("cor", size = 3)),
    lower = list(continuous = wrap("points", size = 0.6, alpha = 0.3)),
    diag  = list(continuous = wrap("densityDiag", alpha = 0.5)),
    columnLabels = c("Age", "BMI z", "Sys BP", "Dia BP", "log Lp(a)", "Lifestyle")
  ) +
  theme_minimal(base_size = 10)
p_pairs

```

# Descriptive Tables for Manuscript

```{r}
# Define footnote text explaining the composite lifestyle risk score
lifestyle_fn <- paste(
  "Composite lifestyle risk score (0-4): one point each for insufficient",
  "physical activity (below WHO), poor diet (Mediterranean diet score <=3),",
  "excess screen time (above age cut-off), and short sleep (below age cut-off).",
  "0 = ideal phenotype; 4 = all four adverse factors present. Tiers: Ideal (0-1), Moderate (2), Poor (3-4)."
)

# Table 1 — Overall sample characteristics
table1 <- df_reg %>%
  dplyr::select(age, sex, who_bmi_for_age_z, bp_sys, bp_dia,
                blood_value_lpa, card_risk_fam_combined, comp_score) %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      blood_value_lpa ~ "{median} ({p25}, {p75}); {mean} ({sd})"
    ),
    digits = list(all_continuous() ~ 1, who_bmi_for_age_z ~ 2),
    label = list(
      age ~ "Age (years)",
      sex ~ "Sex",
      who_bmi_for_age_z ~ "BMI z-score",
      bp_sys ~ "Systolic BP (mmHg)",
      bp_dia ~ "Diastolic BP (mmHg)",
      blood_value_lpa ~ "Lp(a), mg/L",
      card_risk_fam_combined ~ "Family history of CVD",
      comp_score ~ "Lifestyle risk score (0-4)"
    ),
    missing = "ifany"
  ) %>%
  add_n() %>%
  modify_header(label = "**Characteristic**") %>%
  modify_caption(paste("**Table 1. Sample Characteristics.**", lifestyle_fn)) %>%
  bold_labels()

# Table 2 — Characteristics stratified by lifestyle tier
table2 <- df_reg %>%
  dplyr::select(age, sex, who_bmi_for_age_z, bp_sys, bp_dia,
                blood_value_lpa, card_risk_fam_combined, lifestyle_tier) %>%
  tbl_summary(
    by = lifestyle_tier,
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      blood_value_lpa ~ "{median} ({p25}, {p75}); {mean} ({sd})"
    ),
    digits = list(all_continuous() ~ 1, who_bmi_for_age_z ~ 2),
    label = list(
      age ~ "Age (years)",
      sex ~ "Sex",
      who_bmi_for_age_z ~ "BMI z-score",
      bp_sys ~ "Systolic BP (mmHg)",
      bp_dia ~ "Diastolic BP (mmHg)",
      blood_value_lpa ~ "Lp(a), mg/L",
      card_risk_fam_combined ~ "Family history of CVD"
    ),
    missing = "ifany"
  ) %>%
  add_n() %>% add_p() %>% add_overall() %>%
  modify_header(label = "**Characteristic**") %>%
  modify_caption("**Table 2. Sample Characteristics by Lifestyle Tier**") %>%
  bold_labels()

# Define labels for regression models
lab_main <- list(
  lifestyle_tier ~ "Lifestyle Tier",
  log_lpa ~ "Log Lp(a)",
  card_risk_fam_combined ~ "Family history of CVD",
  who_bmi_for_age_z ~ "BMI z-score",
  age ~ "Age (years)",
  sex ~ "Sex"
)

# Table 3 — Main effects models
table3 <- tbl_merge(
  tbls = list(
    tbl_regression(sys_main, intercept = FALSE, label = lab_main) %>%
      add_glance_source_note(include = c(nobs, r.squared, adj.r.squared)),
    tbl_regression(dia_main, intercept = FALSE, label = lab_main) %>%
      add_glance_source_note(include = c(nobs, r.squared, adj.r.squared))
  ),
  tab_spanner = c("**Systolic BP**", "**Diastolic BP**")
) %>%
  modify_caption("**Table 3. Main Effects Predictors of Blood Pressure**")

# Table 4 — Interaction: Lifestyle x Lp(a)
table4 <- tbl_merge(
  tbls = list(
    tbl_regression(sys_lpa_int, intercept = FALSE, label = lab_main) %>%
      add_glance_source_note(include = c(nobs, r.squared, adj.r.squared)),
    tbl_regression(dia_lpa_int, intercept = FALSE, label = lab_main) %>%
      add_glance_source_note(include = c(nobs, r.squared, adj.r.squared))
  ),
  tab_spanner = c("**Systolic BP**", "**Diastolic BP**")
) %>%
  modify_caption("**Table 4. Lifestyle × Lp(a) Interaction on Blood Pressure**")

# Table 5 — Interaction: Lifestyle x Family History
table5 <- tbl_merge(
  tbls = list(
    tbl_regression(sys_fam_int, intercept = FALSE, label = lab_main) %>%
      add_glance_source_note(include = c(nobs, r.squared, adj.r.squared)),
    tbl_regression(dia_fam_int, intercept = FALSE, label = lab_main) %>%
      add_glance_source_note(include = c(nobs, r.squared, adj.r.squared))
  ),
  tab_spanner = c("**Systolic BP**", "**Diastolic BP**")
) %>%
  modify_caption("**Table 5. Lifestyle × Family History Interaction on Blood Pressure**")

# Define labels for ordinal regression models
lab_ord <- list(
  comp_score_f          ~ "Lifestyle risk score",
  log_lpa               ~ "Log Lp(a)",
  card_risk_fam_combined ~ "Family history of CVD",
  age                   ~ "Age (years)",
  sex                   ~ "Sex",
  who_bmi_for_age_z     ~ "BMI z-score"
)

# Table 6 — Percentile-based BP (Ordinal Models)
table6 <- tbl_merge(
  tbls = list(
    tbl_regression(m_pctl_sys, intercept = FALSE, exponentiate = TRUE, label = lab_ord) %>% 
      add_glance_source_note(),
    tbl_regression(m_pctl_dia, intercept = FALSE, exponentiate = TRUE, label = lab_ord) %>% 
      add_glance_source_note()
  ),
  tab_spanner = c("**Systolic percentile**", "**Diastolic percentile**")
) %>%
  modify_caption("**Table 6. Lifestyle Score and Ordinal Percentile-Based Blood Pressure (Odds Ratios)**")

# Export all manuscript tables to a single Word document
all_tables <- list(
  "Table 1" = table1,  "Table 2" = table2,  "Table 3" = table3,
  "Table 4" = table4,  "Table 5" = table5,  "Table 6" = table6
)

tables_docx <- purrr::map(all_tables, as_flex_table)
do.call(save_as_docx, c(tables_docx, path = "manuscript_tables.docx"))

cat("Tables exported successfully to manuscript_tables.docx\n")
```

# Participant Flow Diagram

```{r}
# Calculate the drop for missing covariates in the final regression dataset
n_missing_covariates <- nrow(df) - nrow(df_reg)
n_final_cc <- nrow(df_reg)

# Build the participant flow chart using Graphviz syntax
graph_text <- glue::glue("
digraph flowchart {{
  graph [layout = dot, rankdir = TB]
  
  # Define node styles
  node [shape = box, fontname = Helvetica, fontsize = 12, width = 3.5, style = filled, fillcolor = '#F9F9F9', color = '#555555']
  edge [fontname = Helvetica, fontsize = 10, color = '#555555']
  
  # Inclusion nodes (Main vertical spine)
  total [label = 'Total participants in raw dataset\\nn = {n_total}']
  blood [label = 'Blood tested\\nn = {n_blood}']
  lpa   [label = 'Valid Lp(a) measurement\\nn = {n_lpa}']
  age   [label = 'Aged 9-18 years\\nn = {n_age}']
  sex   [label = 'Sex: Male/Female\\nn = {n_sex}']
  final [label = 'Complete cases for analysis\\n(No missing covariates)\\nn = {n_final_cc}', fillcolor = '#E2F0D9']
  
  # Exclusion nodes (Branching off to the right)
  node [fillcolor = '#FCE4D6', width = 2.8]
  excl_blood [label = 'Excluded: No blood test\\nn = {n_total - n_blood}']
  excl_lpa   [label = 'Excluded: Missing Lp(a)\\nn = {n_blood - n_lpa}']
  excl_age   [label = 'Excluded: Outside age 9-18\\nn = {n_lpa - n_age}']
  excl_sex   [label = 'Excluded: Diverse/Missing sex\\nn = {n_age - n_sex}']
  excl_cc    [label = 'Excluded: Missing lifestyle or BP data\\nn = {n_missing_covariates}']
  
  # Force horizontal alignment for exclusions
  {{ rank = same; blood; excl_blood }}
  {{ rank = same; lpa; excl_lpa }}
  {{ rank = same; age; excl_age }}
  {{ rank = same; sex; excl_sex }}
  {{ rank = same; final; excl_cc }}
  
  # Draw vertical spine arrows
  total -> blood
  blood -> lpa
  lpa -> age
  age -> sex
  sex -> final
  
  # Draw exclusion branch arrows
  total -> excl_blood
  blood -> excl_lpa
  lpa -> excl_age
  age -> excl_sex
  sex -> excl_cc
}}
")

# Render the graph
flow_chart <- DiagrammeR::grViz(graph_text)
flow_chart

# Export the flowchart to a high-resolution PNG
flow_chart %>%
  DiagrammeRsvg::export_svg() %>%
  charToRaw() %>%
  rsvg::rsvg_png("flow_chart.png", width = 1500)

cat("Exported flow_chart.png successfully!\n")
```


# Final Export

```{r}
have <- function(nm) exists(nm, envir = .GlobalEnv)

lpa_pos <- df_reg %>% filter(blood_value_lpa > 0)

# 1. Missingness & Mediation tables
if (have("missing_summary")) {
  ft_missing <- missing_summary %>%
    filter(n_missing > 0) %>%
    flextable() %>%
    set_caption("Missingness by Variable (Analysis Sample)") %>%
    autofit()
}

if (have("paths")) {
  ft_mediation <- bind_rows(paths, .id = "Path") %>%
    dplyr::select(Path, term, estimate, std.error, statistic, p.value) %>%
    mutate(across(c(estimate, std.error, statistic), ~round(.x, 3)),
           p.value = format.pval(as.numeric(p.value), digits = 3, eps = 0.001)) %>%
    flextable() %>%
    set_caption("Mediation Analysis Paths (Lifestyle -> BMI -> BP)") %>%
    autofit()
}

# 2. Non-parametric test tables
w_fh <- wilcox.test(blood_value_lpa ~ card_risk_fam_combined,
                    data = lpa_pos %>% drop_na(card_risk_fam_combined))
ft_wilcox_fh <- lpa_pos %>% drop_na(card_risk_fam_combined) %>% group_by(`Family history` = card_risk_fam_combined) %>%
  summarise(N = n(), `Median (IQR)` = sprintf("%.1f (%.1f, %.1f)", median(blood_value_lpa), quantile(blood_value_lpa, .25), quantile(blood_value_lpa, .75)), .groups = "drop") %>%
  flextable() %>% set_caption("Lp(a) by Family History of CVD (Wilcoxon rank-sum)") %>%
  add_footer_lines(sprintf("W = %.0f, p = %s", w_fh$statistic, format.pval(w_fh$p.value, digits = 3, eps = 0.001))) %>% autofit()

k_tier <- kruskal.test(blood_value_lpa ~ lifestyle_tier, data = lpa_pos)
ft_kruskal_tier <- lpa_pos %>% drop_na(lifestyle_tier) %>% group_by(`Lifestyle tier` = lifestyle_tier) %>%
  summarise(N = n(), `Median (IQR)` = sprintf("%.1f (%.1f, %.1f)", median(blood_value_lpa), quantile(blood_value_lpa, .25), quantile(blood_value_lpa, .75)), .groups = "drop") %>%
  flextable() %>% set_caption("Lp(a) by Lifestyle Tier (Kruskal-Wallis)") %>%
  add_footer_lines(sprintf("chi-squared = %.2f, df = %d, p = %s", k_tier$statistic, k_tier$parameter, format.pval(k_tier$p.value, digits = 3, eps = 0.001))) %>% autofit()

pw <- pairwise.wilcox.test(lpa_pos$blood_value_lpa, lpa_pos$lifestyle_tier, p.adjust.method = "bonferroni")
ft_pairwise <- as.data.frame(pw$p.value) %>% tibble::rownames_to_column("Group 1") %>% pivot_longer(-`Group 1`, names_to = "Group 2", values_to = "p_adj") %>% drop_na(p_adj) %>% mutate(`Adjusted p` = format.pval(p_adj, digits = 3, eps = 0.001)) %>% dplyr::select(`Group 1`, `Group 2`, `Adjusted p`) %>% flextable() %>% set_caption("Pairwise Lp(a) Comparisons Between Lifestyle Tiers (Bonferroni)") %>% autofit()

make_anova_ft <- function(model_list, labels, cap) {
  broom::tidy(do.call(anova, model_list)) %>% mutate(Model = labels) %>% dplyr::select(Model, df, `Sum Sq` = sumsq, `F` = statistic, `p-value` = p.value) %>%
    mutate(`Sum Sq` = round(`Sum Sq`, 2), `F` = ifelse(is.na(`F`), "—", as.character(round(`F`, 2))), `p-value` = ifelse(is.na(`p-value`), "—", format.pval(`p-value`, digits = 3, eps = 0.001))) %>% flextable() %>% set_caption(cap) %>% autofit()
}
ft_anova_sys <- make_anova_ft(
  list(m1_sys, m2_sys), 
  c("M1: Base", "M2: + Lifestyle & Family Hx"), 
  "Model Comparison - Systolic BP (nested F-test)"
)
ft_anova_dia <- make_anova_ft(
  list(m1_dia, m2_dia), 
  c("M1: Base", "M2: + Lifestyle & Family Hx"), 
  "Model Comparison - Diastolic BP (nested F-test)"
)

# ALL Figures (Standard + Complex + Forest)
figure_names <- c(
  "Blood pressure by lifestyle score"      = "p_bp_lifestyle",
  "Systolic BP by family history"          = "p_bp_famhist",
  "BMI z-score vs Lp(a)"                   = "p_bmi_lpa",
  "Lp(a) across age"                       = "p_lpa_age",
  "Family history across age"              = "p_famhist_age",
  "Blood pressure across age"              = "p_bp_age",
  "Systolic BP across lifestyle score"     = "p_bp_score_scatter",
  "Systolic BP vs BMI z-score"             = "p_bp_bmi",
  "Log Lp(a) vs systolic BP"               = "p_lpa_bp",
  "Density of log Lp(a) by family history" = "p_lpa_density_fh",
  "Correlation matrix"                     = "p_corr",
  "Systolic BP by lifestyle components"    = "p_bp_components",
  "Lp(a) spread (whole dataset)"           = "p_lpa_spread_all",
  "Lp(a) raw vs log distribution"          = "p_lpa_vs_log",
  "Family history: whole vs analysis"      = "p_fh_compare",
  "Lifestyle score spread"                 = "p_lifestyle_spread",
  "Age: included vs excluded"              = "p_excl_age",
  "BMI: included vs excluded"              = "p_excl_bmi",
  "BP: included vs excluded"               = "p_excl_bp",
  "Sex: included vs excluded"              = "p_excl_sex",
  "Distribution of continuous variables"   = "p_hist_continuous",
  "Distribution of categorical variables"  = "p_bar_categorical",
  "Lp(a) vs continuous variables"          = "p_lpa_vs_continuous",
  "Lp(a) vs categorical variables"         = "p_lpa_vs_categorical",
  "Lp(a) developmental trajectory"         = "p_lpa_trajectory",
  "Lp(a) distribution by sex"              = "p_lpa_density_sex",
  "Lp(a) by family history (boxplot)"      = "p_lpa_famhist_box",
  "Lp(a) by lifestyle tier"                = "p_lpa_tier",
  "Spearman correlation heatmap"           = "p_spearman_heatmap",
  "BMI z-score by sex"                     = "p_bmi_by_sex",
  "BMI z-score vs Lp(a) (loess)"           = "p_bmi_vs_lpa",
  "Coefficient plot (systolic models)"     = "p_coef_sys",
  "Lifestyle x family history interaction" = "p_interaction",
  "Elevated Lp(a) by lifestyle tier"       = "p_lpa_elevated_tier",
  "Blood Pressure Across Age by Sex"       = "p_bp_age_sex",
  "Lp(a) vs BP Split by Tier"              = "p_lpa_bp_tier",
  "Raincloud: Systolic BP by Lifestyle"    = "p_bp_raincloud",
  "Bubble Chart: Age, BP, Lp(a), Tier"     = "p_bubble",
  "Pairs Plot (GGally)"                    = "p_pairs",
  "Forest Plot: Binary BP Models"          = "p_forest_binary",
  "Forest Plot: Multinomial BP Models"     = "p_forest_multi"
)

# ALL gtsummary tables
gtsummary_tables <- c(
  "Bias Check: Included vs Excluded"                 = "tab_bias",
  "Table 1. Sample characteristics"                  = "table1",
  "Table 2. By lifestyle tier"                       = "table2",
  "Table 3. Main Effects Predictors of BP"           = "table3",
  "Table 4. Lifestyle × Lp(a) Interaction"           = "table4",
  "Table 5. Lifestyle × Family History Interaction"  = "table5",
  "Table 6. Ordinal Percentile-Based BP"             = "table6"
)

# ALL Native flextable tables
test_fts <- c(
  "Missingness Summary"                            = "ft_missing",
  "Mediation Paths"                                = "ft_mediation",
  "Variance Inflation Factors"                     = "ft_vif",
  "Joint Interaction Tests"                        = "ft_int_tests",
  "Minimum Detectable Interaction Effects"         = "ft_mde",
  "Sensitivity Analyses (ANOVA)"                   = "ft_sens_tests",
  "Lp(a) by family history (Wilcoxon)"             = "ft_wilcox_fh",
  "Lp(a) by lifestyle tier (Kruskal-Wallis)"       = "ft_kruskal_tier",
  "Pairwise tier comparisons"                      = "ft_pairwise",
  "Model comparison - systolic"                    = "ft_anova_sys",
  "Model comparison - diastolic"                   = "ft_anova_dia",
  "S1. Linear BP models (estimate + 95% CI)"       = "ft_supp_linear",
  "S2. Composite-score models (estimate + 95% CI)" = "ft_supp_composite",
  "S3. Composite vs components (nested F-test)"    = "ft_comp_vs_components"
)

missing_figs <- names(figure_names)[!vapply(figure_names, have, logical(1))]
if (length(missing_figs)) warning("FIGURES NOT EXPORTED: ", paste(missing_figs, collapse = ", "))

missing_gt <- names(gtsummary_tables)[!vapply(gtsummary_tables, have, logical(1))]
if (length(missing_gt)) warning("GT TABLES NOT EXPORTED: ", paste(missing_gt, collapse = ", "))

missing_ft <- names(test_fts)[!vapply(test_fts, have, logical(1))]
if (length(missing_ft)) warning("FLEXTABLES NOT EXPORTED: ", paste(missing_ft, collapse = ", "))

figure_names     <- figure_names[vapply(figure_names, have, logical(1))]
gtsummary_tables <- gtsummary_tables[vapply(gtsummary_tables, have, logical(1))]
test_fts         <- test_fts[vapply(test_fts, have, logical(1))]

# Save figures as 300-dpi PNGs
dir.create("figures", showWarnings = FALSE)
fig_paths <- character(0)
for (cap in names(figure_names)) {
  path <- file.path("figures", paste0(gsub("[^A-Za-z0-9]+", "_", cap), ".png"))
  ok <- try(ggsave(path, get(figure_names[[cap]]), width = 12, height = 6, dpi = 300, bg = "white"), silent = TRUE)
  if (!inherits(ok, "try-error")) fig_paths[cap] <- path else warning("Figure failed: ", cap)
}
figure_names <- figure_names[names(fig_paths)]

# Build the Word document
doc <- read_docx()

if (file.exists("flow_chart.png")) {
  doc <- doc %>%
    body_add_par("Participant Flow", style = "heading 1") %>%
    body_add_img("flow_chart.png", width = 6, height = 6) %>%
    body_add_par("", style = "Normal")
}

doc <- doc %>% body_add_par("Tables", style = "heading 1")
for (cap in names(gtsummary_tables)) {
  doc <- doc %>%
    body_add_par(cap, style = "heading 2") %>%
    body_add_flextable(as_flex_table(get(gtsummary_tables[[cap]]))) %>%
    body_add_par("", style = "Normal")
}

doc <- doc %>% body_add_par("Supplementary & Test Tables", style = "heading 1")
for (cap in names(test_fts)) {
  doc <- doc %>%
    body_add_par(cap, style = "heading 2") %>%
    body_add_flextable(get(test_fts[[cap]])) %>%
    body_add_par("", style = "Normal")
}

doc <- doc %>% body_add_par("Figures", style = "heading 1")
for (cap in names(figure_names)) {
  doc <- doc %>%
    body_add_par(cap, style = "heading 2") %>%
    body_add_img(fig_paths[cap], width = 7.5, height = 3.75) %>%
    body_add_par("", style = "Normal")
}

print(doc, target = "manuscript_full.docx")

# Save objects to regenerate later
saveRDS(
  list(
    df    = df, 
    df_reg = df_reg,
    models = mget(ls(.GlobalEnv, pattern = "^m[0-9]|^m_|^sys_|^dia_"), envir = .GlobalEnv, ifnotfound = list(NA))
  ), 
  "analysis_objects.rds"
)
```
